\section{Authors Contribution}\label{authors-contribution}

The manuscript was prepared exclusively by the named authors. The first author made the primary contribution to the development of the paper, including the selection of the research topic, comprehensive engagement with the contemporary literature, formulation of the review framework, articulation and discussion of the central concepts, development of visual materials, and synthesis of the final report. The second author contributed by proofreading the manuscript, revising minor sections, and enhancing its stylistic quality.

\section{Funding Information}\label{funding-information}

No financial support of any form, cash or kind, were either sought or utilized for research planning, scoping, executing and writing.

\section{Ethical Statement}\label{ethical-statement}

This manuscript is a systematic review of existing published research and does not involve new data collection from human or animal participants. Therefore, specific ethics committee approval was not sought. All literary sources are properly cited, and the work is an original analysis.

Figures and tables were created either with primarily collected data or secondary data, which when used has been properly credited. Semi-commercial or openly sourced media (image, graphs, videos, news) when reproduced are attributed as such.

\section{Acknowledgement}\label{acknowledgement}

Authors are grateful to their respective institutions of affiliation for their constant encouragement, and to their families for members' unconditional support and patience.
